Keyword and Collocation analysis on India-related text of Natural History

### 2023-06-19 paper_quarto.qmd
tibble update

As mentioned, the digitized text with geographical annotation is available through [TOPOSText](https://topostext.org/work/148 "Check Natural History on ToposText") project, I further scraped the full text and exported them in .txt as a \![reference corpus\]{#ref-corpus}, and also exported those with annotation of coordinates in a range of Indian subcontinent as geographically related texts to India as a \![target corpus\]{#tar-corpus}. The scraping code can be accessed in the link.

@@

> The @ref-corpus consists of all texts in the encyclopedia, divided by paragraphs, has `r prettyNum(n_tokens(ref_flist))` tokens and `r n_types(ref_flist)` types, with the type-token ratio of `r round(n_types(ref_flist)/n_tokens(ref_flist), 2)`.
>
> And the @tar-corpus consists of all text related to Indian subcontinent (with coordinates in range of 8°4'N-37°6'N and 68°7'E to 97°25'E) , has `r prettyNum(n_tokens(tar_flist))` tokens and `r n_types(tar_flist)` types, with the type-token ratio of `r round(n_types(tar_flist)/n_tokens(tar_flist), 2)`.
>
> The tokens are separated by white space and in the analysis of this paper, all the punctuation marks are removed.

@@

@tbl-kwtables shows the top 30 keywords in Indian related texts comparing to other context, respectively sorted by PMI and G_signed.

::: {#tbl-kwtables .panel-tabset}
## Sorted by PMI

```{r}
#| warning: false
#| echo: false

@@

```{r}
#| warning: false
#| echo: false

@@

@tbl-coltable_PMI and @tbl-coltable_Gsigned shows the top 30 keywords in Indian related texts comparing to other context, respectively sorted by PMI and G_signed.

@@

```{r}
#| label: tbl-coltable_PMI
#| tbl-cap-location: top
#| tbl-cap: Top 30 Keywords on Indian Related Text in Natural History (sorted by PMI)
#| warning: false
#| echo: false
top_scores_colloc %>% 
  as_tibble() %>%
  select(type, a, PMI, G_signed) %>% # select 4 columns
  arrange(desc(PMI)) %>%        # sort by G_signed (descending)  
  head(30) %>%                       # select top 30 rows
  kbl(col.names = c("Type", "Frequency", "PMI", "Signed G^2"))%>%
  kable_minimal() %>% 
  scroll_box(height = "400px")

>>>>

As mentioned, the digitized text with geographical annotation is available through [TOPOSText](https://topostext.org/work/148 "Check Natural History on ToposText") project, I further scraped the full text and exported them in .txt as a **reference corpus**, and also exported those with annotation of coordinates in a range of Indian subcontinent as geographically related texts to India as a **target corpus**. The scraping code can be accessed in the link.

@@

The **reference corpus** consists of all texts in the encyclopedia, divided by paragraphs, has `r prettyNum(n_tokens(ref_flist))` tokens and `r n_types(ref_flist)` types, with the type-token ratio of `r round(n_types(ref_flist)/n_tokens(ref_flist), 2)`.

And the **target corpus** consists of all text related to Indian subcontinent (with coordinates in range of *8°4'N-37°6'N and 68°7'E to 97°25'E*) , has `r prettyNum(n_tokens(tar_flist))` tokens and `r n_types(tar_flist)` types, with the type-token ratio of `r round(n_types(tar_flist)/n_tokens(tar_flist), 2)`.

The tokens are separated by white space and in the analysis of this paper, all the punctuation marks are removed.

@@

@tbl-kwtable_PMI and @tbl-kwtable_Gsigned shows the top 30 keywords in Indian related texts comparing to other context, respectively sorted by PMI and G_signed.

```{r}
#| warning: false
#| echo: false
#| label: tbl-kwtable_PMI
#| tbl-cap-location: top
#| tbl-cap: Top 30 Keywords on Indian Related Text in Natural History (sorted by PMI)

@@

```{r}
#| warning: false
#| echo: false
#| label: tbl-kwtable_Gsigned
#| tbl-cap-location: top
#| tbl-cap: Top 30 Keywords on Indian Related Text in Natural History (sorted by G_Signed)

@@

@tbl-coltable_PMI and @tbl-coltable_Gsigned shows the top 30 collocates to the word "india" in the whole text, respectively sorted by PMI and G_signed.

@@

```{r}
#| label: tbl-coltable_PMI
#| tbl-cap-location: top
#| tbl-cap: Top 30 Keywords on Indian Related Text in Natural History (sorted by PMI)
#| warning: false
#| echo: false
top_scores_colloc %>% 
  as_tibble() %>%
  select(type, a, PMI, G_signed) %>% # select 4 columns
  arrange(desc(PMI)) %>%        # sort by G_signed (descending)  
  head(30) %>%                       # select top 30 rows
  kbl(col.names = c("Type", "Frequency", "PMI", "Signed G^2^"))%>%
  kable_minimal() %>% 
  scroll_box(height = "400px")
